The Unicode Cookbook \linebreak for Linguists

### 2018-08-09 book/chapters/introduction.tex
Post release updates (#44)
* update gitignore

* minor edits in introduction

* small caps in introduction

* minor edits to chapter 2 unicode approach

* corrections chapter 3 unicode pitfalls

* corrections chapter 4 IPA

* layout of tables in chapter 5

* typo in Chapter 5

* update bibliography

* more latex gitignore

* addition to Chapter 7 orthography profiles

* corrections to chapter 8 implementation

* Updated tex and pdf files

* requested changes

* fix alignment on p.107

* change bash explanation

* edits in last paragraph; copy up the cookbook pdf

Breaking it down further, a script consists of \textsc{graphemes}, which are writing 
system-specific minimally distinctive symbols (see below). Graphemes may consist of one or more 
\textsc{characters}. The term `character' is overladen. In the linguistic terminology of writing
systems, a character is a general term for any self-contained element
in a writing system. A second interpretation is used as a conventional term for a unit in the Chinese writing
system \citep{Daniels1996}. In technical terminology, a character}
refers to the electronic encoding of a component in a writing system that has semantic 
value (see Section \ref{character-encoding-system}). Thus in this work we must navigate 
between the general linguistic and technical terms for \textsc{character} 
and \textsc{grapheme} because of how these notions are defined and how they relate at the intersection 
between the International Phonetic Alphabet and the Unicode Standard (Chapter \ref{ipa-meets-unicode}).

>>>>

Breaking it down further, a script consists of \textsc{graphemes}, which are writing 
system-specific minimally distinctive symbols (see below). Graphemes may consist of one or more 
\textsc{characters}. The term `character' is overladen. In the linguistic terminology of writing
systems, a character is a general term for any self-contained element
in a writing system. A second interpretation is used as a conventional term for a unit in the Chinese writing
system \citep{Daniels1996}. In technical terminology, a character
refers to the electronic encoding of a component in a writing system that has semantic 
value (see Section \ref{character-encoding-system}). Thus in this work we must navigate 
between the general linguistic and technical terms for \textsc{character} 
and \textsc{grapheme} because of how these notions are defined and how they relate at the intersection 
between the International Phonetic Alphabet and the Unicode Standard (Chapter \ref{ipa-meets-unicode}).

### 2018-08-09 book/chapters/orthography_profiles.tex
Post release updates (#44)
* update gitignore

* minor edits in introduction

* small caps in introduction

* minor edits to chapter 2 unicode approach

* corrections chapter 3 unicode pitfalls

* corrections chapter 4 IPA

* layout of tables in chapter 5

* typo in Chapter 5

* update bibliography

* more latex gitignore

* addition to Chapter 7 orthography profiles

* corrections to chapter 8 implementation

* Updated tex and pdf files

* requested changes

* fix alignment on p.107

* change bash explanation

* edits in last paragraph; copy up the cookbook pdf

\begin{enumerate}
	\def\labelenumi{A\arabic{enumi}.} 
	\item \textsc{A profile is a unicode utf-\scalebox{0.8}{8} encoded text file} 
	   % normalized following NFC (or NFD if specified in the metadata)
       that includes information pertinent to the orthography.\footnote{See 
	   Section~\ref{pitfall-file-formats} in which we suggest to use NFC, 
	   no-BOM and LF line breaks because of the pitfalls they avoid. A keen reviewer notes, however, that specifying 
	   a convention for line endings and BOM is overly strict because most 
	   computing environments (now) transparently handle both alternatives. 
	   For example, using Python a file can be decoded using the encoding 
	   ``utf-8-sig'', which strips away the BOM (if present) and reads 
	   an input full in text mode, so that both line feed variants ``LF'' and 
	   ``CRLF'' will be stripped.}

>>>>

\begin{enumerate}
	\def\labelenumi{A\arabic{enumi}.} 
	\item \textsc{A profile is a unicode utf-\scalebox{0.8}{8} encoded text file} 
	   % normalized following NFC (or NFD if specified in the metadata)
       that includes information pertinent to the orthography.\footnote{See 
	   Section~\ref{pitfall-file-formats} in which we suggest to use NFC, 
	   no-BOM and LF line breaks because of the pitfalls they avoid. Specifying 
	   a convention for line endings and BOM is often overly strict because most 
	   computing environments (now) transparently handle both alternatives. 
	   For example, using Python a file can be decoded using the encoding 
	   ``utf-8-sig'', which strips away the BOM (if present) and reads 
	   an input full in text mode, so that both line feed variants ``LF'' and 
	   ``CRLF'' will be stripped. However, note that most shells (e.g. bash) will not 
	   behave properly with CRLF line endings.}
